Why Donors Donate?

### 2020-09-13 analysis/05_market_simulator.Rmd
Testing Simulator with Excel Results. Something might be wrong with how Org 1 is computed.

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV06.xlsx"))

@@

# Org Reactive Element
df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1

@@

    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1

@@

    beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1

@@

<!-- Persona Inputs -->
```{r persona betas}

@@

p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)

@@

p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)

# 
# exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)

@@

p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)

# 
# exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)

@@

@@

@@

@@

>>>>

# Persona Data from Market Simulator Workbook
persona_data <- readxl::read_xlsx(here('analysis', 'output', "persona_configV07.xlsx"))

# Org Data from Market Simulator Workbook
org_data <- readxl::read_xlsx(here('analysis', 'output', "org_config.xlsx"))

@@

# Org Reactive Element
df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    # beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$org1_id] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$ai_value[beta$levels %in% input$org2_id] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    # beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ai_value[beta$levels %in% input$org3_id] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    # beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$ai_value[beta$levels %in% input$org4_id] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

    beta_persona$p1_value[beta_persona$levels == 'Intercept'] <- 1

@@

    beta_persona$p2_value[beta_persona$levels == 'Intercept'] <- 1

@@

    beta_persona$p3_value[beta_persona$levels == 'Intercept'] <- 1

@@

<!-- Persona Inputs -->
```{r Manual Testing Matrix Multiplication}

@@

# matrix multiplication between persona data and betas
beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)

@@

# matrix multiplication between persona data and betas
beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)

@@

# matrix multiplication between persona data and betas
beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)

# Orgnization
org1 <- org_data[,2]

org2 <- org_data[,3]

org3 <- org_data[,4]

org4 <- org_data[,5]

# Expected utility matrix multiplication between computed persona betas and org data for persona 1
org1_exp_util1 <- exp(t(org1) %*% as.matrix(beta1))
org2_exp_util1 <- exp(t(org2) %*% as.matrix(beta1))
org3_exp_util1 <- exp(t(org3) %*% as.matrix(beta1))
org4_exp_util1 <- exp(t(org4) %*% as.matrix(beta1))

# Market Share computation from expected utilities between organization
org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)

# org1_exp_util2 <- exp(t(org1) %*% as.matrix(p_beta2))
# org2_exp_util2 <- exp(t(org2) %*% as.matrix(p_beta2))
# org3_exp_util2 <- exp(t(org3) %*% as.matrix(p_beta2))
# org4_exp_util2 <- exp(t(org4) %*% as.matrix(p_beta2))
# 
# 
# org1_exp_util3 <- exp(t(org1) %*% as.matrix(p_beta3))
# org2_exp_util3 <- exp(t(org2) %*% as.matrix(p_beta3))
# org3_exp_util3 <- exp(t(org3) %*% as.matrix(p_beta3))
# org4_exp_util3 <- exp(t(org4) %*% as.matrix(p_beta3))

@@

selectInput("org1_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("org2_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("org3_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("org4_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))
